---
title: "Running targets on a remote machine over ssh"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Running targets on a remote machine over ssh}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

`crew.ssh` lets a [`targets`](https://docs.ropensci.org/targets/) pipeline run
its work on another machine. The pipeline, the `_targets/` data store, and your
R session all stay where they are; only the computation moves.

You can send the whole pipeline to the remote machine, or route individual
targets there and keep the rest local. Both are covered below.

## Before you start

Three things have to be true.

**1. `ssh` works without a prompt.** `crew.ssh` runs the `ssh` command with
`BatchMode=yes`, so it can never stop to ask for a password or a passphrase.
Check it from a terminal:

```bash
ssh -o BatchMode=yes user@example.com R --version
```

If that prints an R version, you are ready. If it asks for anything, fix the
key setup first: use a key without a passphrase, or load a
passphrase-protected key into `ssh-agent`. Password authentication is not
supported.

`ssh_host` is passed straight to `ssh`, so a `Host` alias from `~/.ssh/config`
works too, and that is the best place to put a jump host, a non-standard port,
or a specific key:

```
Host bigbox
  HostName example.com
  User me
  IdentityFile ~/.ssh/id_ed25519
  ProxyJump bastion.example.com
```

```{r}
crew.ssh::crew_controller_ssh(ssh_host = "bigbox")
```

**2. The remote machine has R and `crew`.** It also needs every package your
targets use. Version skew in `mirai` and `nanonext` between the two machines
causes connection failures, so keep those aligned.

**3. You have somewhere writable on the remote machine.** The default is
`/tmp`; see `remote_directory` if that does not suit.

## Send the whole pipeline to the remote machine

Set one controller in `_targets.R`:

```{r}
library(targets)

tar_option_set(
  storage = "main",
  retrieval = "main",
  controller = crew.ssh::crew_controller_ssh(
    ssh_host = "user@example.com",
    workers = 4L
  )
)

list(
  tar_target(index, seq_len(8L)),
  tar_target(piece, slow_function(index), pattern = map(index)),
  tar_target(result, combine(piece))
)
```

`tar_make()` then behaves normally. Targets are dispatched to workers on the
remote machine, results come back over the `ssh` connection, and the data store
stays on your machine.

`workers` is the maximum number of remote R processes. `crew` starts them only
as work demands and lets them exit after `seconds_idle` seconds of inactivity,
so a large `workers` value costs nothing while the pipeline is idle.

## Send only some targets to the remote machine

Long or memory-hungry targets often deserve the big machine while everything
else is faster to run locally. Combine controllers with
`crew::crew_controller_group()` and pick one per target.

Give each controller a `name`, set the default with `tar_option_set()`, and
override it on the targets that should go elsewhere:

```{r}
library(targets)

tar_option_set(
  storage = "main",
  retrieval = "main",
  controller = crew::crew_controller_group(
    crew::crew_controller_local(name = "local", workers = 2L),
    crew.ssh::crew_controller_ssh(
      name = "remote",
      ssh_host = "user@example.com",
      workers = 8L
    )
  ),
  resources = tar_resources(crew = tar_resources_crew(controller = "local"))
)

on_remote <- tar_resources(crew = tar_resources_crew(controller = "remote"))

list(
  tar_target(index, seq_len(4L)),
  tar_target(summary_table, quick_summary()),
  tar_target(
    fit,
    expensive_model(index),
    pattern = map(index),
    resources = on_remote
  ),
  tar_target(report, assemble(summary_table, fit))
)
```

`summary_table` and `report` run locally; the `fit` branches run on the remote
machine. Targets with no `resources` of their own fall back to the
`tar_option_set()` default, so the local controller stays the default and only
the targets you mark travel.

## Run workers in a container

`launch_prefix` runs each worker under another command instead of starting
`Rscript` directly, which is how a worker runs inside a container. The remote
machine then needs only `ssh` and a container runtime, and the package versions
a fit sees are fixed by the image rather than by whatever else is installed
there, so other work on that machine cannot change them underneath you.

```{r}
crew_controller_ssh(
  ssh_host = "user@example.com",
  launch_prefix = c(
    "docker", "run", "--rm",
    "--network=host",
    "--volume", "/tmp:/tmp",
    "my-image"
  ),
  workers = 4L,
  # Starting a container and attaching packages takes longer than the plain
  # Rscript start the default allows for.
  seconds_launch = 300
)
```

Each element is quoted for the remote shell separately, so an element may
contain spaces (`"--volume", "/home/my data:/data"`) without being split into
two arguments.

Two of those options are not optional.

`--network=host` is required. The reverse `ssh` tunnel listens on the *remote
machine's* loopback interface, and a container on a bridge network has a
loopback of its own, so a worker there dials a port nothing is listening on.
The symptom is the confusing one from "When something goes wrong" below: a
worker that starts and then never connects. `podman` takes the same flag, and
for `apptainer` it is already the default.

`--volume /tmp:/tmp` is required because the launcher writes each worker's R
script into `remote_directory` (`/tmp` by default) on the remote machine and the
worker reads it back by that same path. Mount whatever you set
`remote_directory` to, at the path it has outside the container. Worker logs are
written by the remote shell rather than by the worker, so `logs()` keeps working
whichever prefix you use.

`directory` sets the working directory of the container runtime on the remote
machine, not the working directory inside the container. Use the runtime's own
option for that (`--workdir` for `docker`).

## Two settings that trip people up

### `storage` and `retrieval` must be `"main"`

Unless the remote machine mounts the same filesystem as your own, set both:

```{r}
tar_option_set(storage = "main", retrieval = "main")
```

`targets` otherwise defaults to `storage = "worker"`, where each worker reads
and writes `_targets/objects/` itself. A worker on another machine writes into
its own filesystem, your session waits for files that never appear, and the
pipeline fails after about a minute with:

```
Error hashing output: timed out after retrying for 65 seconds.
Path _targets/objects/<name> does not exist or has incorrect hash.
File sync timed out.
```

With `"main"`, target data travels over the `ssh` connection along with the
task and your session owns the store.

The trade-off is that every input and result crosses the network. That is a
good deal for targets that are slow to compute and modest in size, and a poor
one for targets that do little to a lot of data.

Because the remote machine has its own filesystem, a target that reads or
writes a file by path only works if that path exists *there*. Ordinary
in-memory targets need nothing extra.

If the remote machine *does* mount your project directory, pass
`directory = "/path/to/project"` so workers start in it, and leave `storage`
and `retrieval` at their defaults.

### Every package in `packages` must exist on the remote machine

`tar_option_set(packages = ...)` defaults to whatever is attached when
`_targets.R` is sourced, and `targets` loads all of them on each worker. A
package that is attached locally but missing remotely fails the pipeline with:

```
could not find packages <name> in library paths
```

Set `packages` explicitly to the packages your targets actually need:

```{r}
tar_option_set(packages = c("dplyr", "mgcv"))
```

## When something goes wrong

The most confusing failure is a worker that starts and then never connects.
The reason is almost always in the worker's own output, which `crew.ssh` keeps
in a log file per worker on the remote machine:

```{r}
controller <- crew.ssh::crew_controller_ssh(ssh_host = "user@example.com")
controller$start()
controller$push(1 + 1)
controller$wait()

cat(controller$launcher$logs(), sep = "\n")
#> ==> /tmp/crew-ssh-9f2c.../worker-1a4b....log <==
#> Error in loadNamespace(x) : there is no package called 'crew'
```

Inside a pipeline, reach the launcher through the controller you built:

```{r}
cat(tar_option_get("controller")$launcher$logs(), sep = "\n")
```

The logs outlive the workers, so they are still readable after a crash. Two
other options help:

* `verbose = TRUE` prints the tunnel command and a line per worker launch.
* `rscript = "/path/to/Rscript"` fixes the common case where `Rscript` is not
  on the `PATH` of a non-interactive `ssh` session. Check with
  `ssh -o BatchMode=yes user@example.com which Rscript`.

## Long-running pipelines and disconnecting

The R session that calls `tar_make()` is the pipeline. It owns the data store,
hands out every task, and hosts the connection the remote workers dial into.
When it exits, the workers exit with it — deliberately, so that a closed laptop
does not leave stray R processes on a shared server.

So you cannot start a pipeline, close your session, and reattach to it later.
What you get instead is that **finished work is never lost**. `targets` commits
each target to the store as it completes, so re-running `tar_make()` skips
everything that finished and re-runs only what was in flight:

```{r}
# Session dies after 5 of 8 branches.
tar_make()

# Later, in a new session:
tar_make()
#> ✔ ended pipeline [39.2s, 4 completed, 5 skipped]
```

For a pipeline that must survive you logging off entirely, run the pipeline
itself on the remote machine rather than driving it from your laptop. Put the
project there, start it detached, and come back to it:

```bash
ssh user@example.com
cd ~/project
nohup Rscript -e 'targets::tar_make()' > run.log 2>&1 &
exit
```

Then reconnect whenever you like and inspect the store in place:

```bash
ssh user@example.com "cd ~/project && Rscript -e 'targets::tar_progress()'"
```

In that arrangement the pipeline and its workers are both remote, so use
`crew::crew_controller_local()` in `_targets.R` — `crew.ssh` is not needed
unless you are fanning work out to *further* machines. Choose based on where
the pipeline needs to live:

| You want | Where the pipeline runs | Controller |
|---|---|---|
| Interactive work, heavy compute elsewhere | Your machine | `crew_controller_ssh()` |
| A run that survives logging off | The remote machine | `crew_controller_local()`, started under `nohup` or `tmux` |

Brief network interruptions are survivable in the first arrangement: the
tunnel tolerates roughly 90 seconds of silence, and `crew.ssh` reopens it if it
does drop, so later workers reconnect without restarting the pipeline.

## How it works

1. The `mirai` dispatcher listens on your loopback interface.
2. `crew.ssh` opens one long-lived `ssh` process with a reverse tunnel
   (`ssh -R`). The remote `sshd` picks a free port, so nothing collides with
   other users.
3. Each worker launch is a short `ssh` call that pipes the worker's R script
   over standard input, starts it detached with `nohup`, and returns its remote
   process ID.
4. Workers dial the remote end of the tunnel instead of your machine's address.
5. The tunnel process holds the write end of its own standard input. When your
   R session ends, however abruptly, the operating system closes that pipe and
   the tunnel exits, which shuts the remote workers down with it.

The practical consequence of step 2 is that your machine never has to be
reachable from the remote one. No inbound firewall rule, no port forwarding,
and no routable address — everything travels inside the `ssh` connection you
were already allowed to make.
